\section{PostgreSQL}

\section{Send query result to file}

copy (select * from db_table) to \'/tmp/consulta\';

\subsection{PSQL Output formatting}
When the query result is to large, psql automatically breaks lines. The output may get hard to read. Use \x to change the visualization. Example of the output:

select * from dda where u_id=24 and dda_is_deleted='f';
-[ RECORD 1 ]------+----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
dda_id             | 1121
u_id               | 24
ab_id              | 10304
dda_type           | CHECKING
dda_status         | PENDING_VERIFICATION
dda_is_deleted     | f
dda_verify_op_id   | 44938
version            | 2

Thanks to (http://stackoverflow.com/questions/9604723/alternate-output-format-for-psql).

\section{Awesome Window Manager}
\label{cap_awesome_wm}
Atention: this document is intended to be mount in a Tex generated document. Some keys or commands will appear inside double ` and double ' in the .tex files and inside double quotes on the pdf file generated in Latex. The correct representation is the one of double quotes, on the pdf file.

\subsection{rc.lua configuration file}
It's originally located at:
	/etc/xdg/awesome/rc.lua

It should be copied do user's home folder to avoid errors on the file syntax. Do:
	\$ mkdir -p ~/.config/awesome
	\$ cp /etc/xdg/awesome/rc.lua ~/.config/awesome/

\subsection{Lock Screen}
First, install xscreensaver.
	\$ sudo apt-get install xscreensaver -y

On the rc.lua file located at ~/.config/awesome/ put the following line under “Standard program” section.
	awful.key({ }, ``F12'', function () awful.util.spawn("xscreensaver-command -lock") end),

Where F12 is the keyboard shortcut to lock your screen. Then, at the end of rc.lua file add the following line to start the xscreensaver application.
	awful.util.spawn_with_shell("xscreensaver -no-splash")

Now, restart awesome window manager and test the screensaver.

Thanks to: (https://mohammadthalif.wordpress.com/2011/04/27/how-to-implement-screen-lock-or-screen-saver-functionality-in-awesome-window-manager/)
